---
fontsize: 11pt
header-includes:
- \usepackage{fancyhdr}
- \setlength{\headheight}{13.59999pt}
- \pagenumbering{gobble}
- \usepackage{helvet}
- \usepackage{tcolorbox}
- \usepackage{pdflscape}
- \usepackage[paper=a4, DIV=17]{typearea}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{hyperref}
geometry: margin=0.75in
output:
  pdf_document:
        df_print: paged
urlcolor: blue
params:
  YEAR: 2024
---

```{r Packages, include=FALSE}
library(sf)
library(ggplot2)
library(tidyverse)
library(lubridate)
library(arcgisbinding)
library(writexl)
library(readr)
library(readxl)
library(janitor)
library(ggspatial)
library(ggrepel)
library(english)
library(kableExtra)
library(ggforce)
library(lwgeom)
library(scales)
library(magrittr)
library(purrr)
library(english)
library(knitr)
library(data.table)
```

```{r Data Fetch, echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='hide'}

##### Prefer Method:  Read Hosted Feature Layer

arc.check_product() ### Checks arcGIS licensing ---> Must have a offline version of this license

#### Early Detection Monitoring

## EDM: Juvenile/Adult Fish
# Site Data
ORIC_Site_FL <- arc.select(arc.open(("https://services.arcgis.com/QVENGdaPbd4LUkLV/arcgis/rest/services/service_c8f005df2d814ee9a6a24999cbbb4f04/FeatureServer/0"))) %>%
  filter(str_detect(Site_ID, as.character(params$YEAR)))

# Fish Count Data
ORIC_Count_FL <- arc.select(arc.open(("https://services.arcgis.com/QVENGdaPbd4LUkLV/arcgis/rest/services/service_c8f005df2d814ee9a6a24999cbbb4f04/FeatureServer/1"))) %>%
  filter(str_detect(Count_ID, as.character(params$YEAR)))

# Fish Individual Data
ORIC_Individual_FL <- arc.select(arc.open(("https://services.arcgis.com/QVENGdaPbd4LUkLV/arcgis/rest/services/service_c8f005df2d814ee9a6a24999cbbb4f04/FeatureServer/2"))) %>%
  filter(str_detect(Individual_ID, as.character(params$YEAR)))
```

```{r Data Shrink, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE, results = 'hide'}
Site_Data <- ORIC_Site_FL
ORIC_Site_FL$EF_ShockTime_seconds <- as.numeric(ORIC_Site_FL$EF_ShockTime_seconds)
Count_Data <- ORIC_Count_FL %>% 
  select(objectid, Count_ID, Count_Common_Name, Number)
Joint_Data <- Site_Data %>% # Calling Site table data
  select(Site_ID, Project, River_Basin, River_Pool,Tributary, Tributary_Pool, Tributary_Pool_Tributary, Gear) %>% # Selected required columns from Site table
  left_join(., ORIC_Count_FL, by = c("Site_ID" = "Count_ID")) %>% # Joining Site table columns and Count table
  select(Project, River_Basin, River_Pool, Tributary, Tributary_Pool, Tributary_Pool_Tributary, Gear, Count_Common_Name, Number) %>%  # Selecting required fields
  mutate(Stream_Name = coalesce(Tributary_Pool_Tributary, Tributary, River_Basin)) %>% # Added new column name and ran ifelse to pull out tributary, main river, tributary of a tributary. is.na to filter any name with na to return Ohio River or Kanawha. !is.na to filter any name that isn't na.
  mutate(Site_Name = coalesce(Tributary_Pool, River_Pool))

Site_Info <- Site_Data %>%
  select(Site_ID, River_Basin, River_Pool,Tributary, Tributary_Pool, Tributary_Pool_Tributary, Gear, Strata) %>%
  mutate(Stream_Name = coalesce(Tributary_Pool_Tributary, Tributary, River_Basin)) %>% # Added new column name and ran ifelse to pull out tributary, main river, tributary of a tributary. is.na to filter any name with na to return Ohio River or Kanawha. !is.na to filter any name that isn't na.
  mutate(Site_Name = coalesce(Tributary_Pool, River_Pool))

EFData <- ORIC_Site_FL %>%
  select(Gear, EF_ShockTime_seconds) %>%
  filter(Gear %in% "Electrofishing") #filtering just efishing gear and shocktime

GearData <- Site_Data %>%
  select(River_Basin, River_Pool,Tributary, Tributary_Pool, Tributary_Pool_Tributary, Gear, Gear_Specific) %>%
  mutate(Gear_Type = if_else(Gear == "Trawl", Gear_Specific, Gear)) %>%
  mutate(Stream_Name = coalesce(Tributary_Pool_Tributary, Tributary, River_Basin)) %>% # Added new column name and ran ifelse to pull out tributary, main river, tributary of a tributary. is.na to filter any name with na to return Ohio River or Kanawha. !is.na to filter any name that isn't na.
  mutate(Site_Name = coalesce(Tributary_Pool, River_Pool)) #gear data with pool sampled

```

\newcommand{\fon}[1]{\fontfamily{#1}\selectfont}

```{=tex}
\begin{tcolorbox}[colback=black,colframe=black,coltext=white,left*=2mm,height=11mm, sharp corners,fontupper=\LARGE\fontfamily{phv}\selectfont\bfseries]
U.S. Fish \& Wildlife Service
\end{tcolorbox}\vspace{-.1cm}
```
\Large\textbf{\fontfamily{phv}\selectfont Aquatic Invasive Species
Annual Report: `r params$YEAR`}\vspace{-.1cm}

\Large\textmd{\textit{Lower Great Lakes FWCO - Ohio River Substation: Williamstown, WV}}\vspace{-.1cm}

\selectfont\large\textbf{Report Creation Date:} `r today()`

\selectfont\large\textbf{Report Data Date Range:}
`r as_date(min(ORIC_Site_FL$Start_DateTime))` to
`r as_date(max(ORIC_Site_FL$Start_DateTime))` \vspace{.5cm}

\selectfont\large\textbf{Introduction}

\selectfont\large This report summarizes data from the second year of an
early detection and monitoring program for invasive carp in the Ohio
River by the LGLFWCO Ohio River Substation based in Williamstown, WV.
This office was created to further the USFWS responsibility of managing
aquatic invasive species. The sampling conducted at this office supports
goal 3 of the USFWS Fisheries and Aquatic Conservation (FAC) Strategic
Plan. This goal has four objectives: Prevent introduction of invasive
species, work with partner agencies to implement an early detection and
rapid response framework, work with partners to prevent the spread of
invasive species, and manage established populations of invasive
species. As invasive carp are a major problem throughout the Mississippi 
River drainage, multiple partnerships have been established to conduct work 
to monitor, remove, and control these established populations across 
different river basins. The Ohio River Invasive Carp Partnership consists 
of state, and federal agencies, as well as Universities that work together 
to tackle goals and objectives derived to monitor, remove, and control invasive
carp. The work this office conducts not only supports the FAC strategic
plan for USFWS, but also supports the goals and objectives of the Ohio
River Basin Invasive Carp Partnership. The focus of this office is early
detection and monitoring of populations in and above the invasion front,
**R.C. Byrd Pool** (RM 279.2), of the Ohio River.

The Ohio River Substation has two project strategies for monitoring and
detecting invasive carp. These strategies are fish community surveys,
and targeted invasive carp monitoring. Fish community survey's focus on
capturing every fish during each sampling event, while targeted invasive
carp monitoring focuses on exclusively capturing invasive carp. Sampling
gear(s) vary for each strategy, but when conducting a targeted invasive
carp survey gear is designed to catch invasive carp (or similarly sized
fish). Additionally, while conducting targeted invasive carp surveys,
any fishes that cannot be identified are captured to confirm species.
For example, a scoop through a school of presumed Gizzard Shad
(*Dorosoma cepedianum*) is collected to confirm no young-of-the-year
invasive carp are present.

Of the `r Site_Info %>% nrow()` total surveys in `r params$YEAR`,
`r ORIC_Site_FL %>% select(Project) %>% filter(Project %in% "Fish Community Survey") %>% nrow()`
(48%) were fish community surveys and
`r ORIC_Site_FL %>% select(Project) %>% filter(Project %in% "Targeted Invasive Carp Monitoring") %>% nrow()`
(52%) were targeted invasive carp monitoring surveys. These early
detection efforts utilized a total of `r Site_Data %>% group_by(Gear) %>% summarise() %>% nrow() %>% words()` unique gear types and were conducted within
`r Site_Info %>% group_by(Site_Name) %>% summarise() %>% nrow() %>% words()`
pools of the Ohio, Kanawha, and Muskingum Rivers:
`r Site_Info %>% group_by(Site_Name) %>% summarise() %>% pluck('Site_Name')`
(Figure 1). \vspace{.5cm}


\pagestyle{fancy}
\fancyhead[L,C]{}
\fancyhead[R]{\textbf{LGLFWCO: Ohio River Substation Annual Report}}
\fancyfoot[L]{\textit {Questions related to this report can be directed to Tyler Gross, Fish Biologist, Supervisor,\\
LGLFWCO Ohio River Substation, Phone: 585-604-0629, Email: tyler\_gross$@$fws.gov}}
\fancyfoot[C]{}
\fancyfoot[R]{\textbf{\thepage}}
\pagenumbering{arabic}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{2pt}

\newpage

```{r Data Manipulation, echo=FALSE, message=FALSE, error=FALSE, warning=FALSE, results = 'hide'}
SamplingData <- ORIC_Site_FL %>% # Calling Site table data
  select(Site_ID, River_Basin, River_Pool,Tributary, Tributary_Pool, Tributary_Pool_Tributary, Start_Latitude, Start_Longitude, Gear, Gear_Specific) %>% # Selected required columns from Site table
   mutate(Gear_Type = if_else(Gear == "Trawl", Gear_Specific, Gear)) %>%
 mutate(Stream_Name = coalesce(Tributary_Pool_Tributary, Tributary, River_Basin)) %>% # Added new column name and ran ifelse to pull out tributary, main river, tributary of a tributary. is.na to filter any name with na to return Ohio River or Kanawha. !is.na to filter any name that isn't na.
  mutate(Site_Name = coalesce(Tributary_Pool, River_Pool))

## Create "Average" Sampling Locations
points <- SamplingData %>%
  select(Site_Name, Start_Longitude, Start_Latitude) %>%
  group_by(Site_Name) %>%
  summarise(Avg_Lat = mean(Start_Latitude), Avg_Lon = mean(Start_Longitude))
sites <- st_as_sf(points, coords = c("Avg_Lon", "Avg_Lat"),
                  crs = 4326, agr = "constant")
```

```{r Map Prep, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE, results='hide', out.width= '100%', fig.align="center", fig.dim=c(7,7)}
## Read in shapefiles
US_sf <- st_read("data/state.shp")
OR_sf <- st_read("data/Riverlines2.shp")

LockandDamdata <- read.csv("LockandDams.csv") # read lock and dam coordinates file

LandDdf <- data.frame(LockandDamdata) # Make csv file a df

sf_use_s2(FALSE)
cropped <- st_crop(US_sf, xmin = -80.6, xmax = -85.18, ymin = 38.1, ymax = 40.00) #cropping the map to sampling area

cropped_XY <- st_zm(cropped, drop = TRUE, what = "ZM") # Dropping Z coordinates
OR_sf_XY <- st_zm(OR_sf, drop = TRUE, what = "ZM") # Dropping Z coordinates

River_map <- ggplot() +
  geom_sf(data = cropped_XY, size = .5, color = "grey60") +
  geom_sf(data = OR_sf_XY, size = 1.25, color = " light blue", fill = NA) +
  geom_sf(data = sites, size = 4, shape = 21, fill = "red3", color = "red1", stroke = 1.25, alpha = .5) +
  geom_point(aes(x = Longitude, y = Latitude), size = 1.5, shape = 21, fill = "black", data = LandDdf) +
   geom_text(data=LandDdf, aes(label=Lock.and.Dam, x = Longitude, y = Latitude), nudge_x = 0.0001, nudge_y = -0.05, color="black", size = 2) +
  annotate(geom = "text", x = -82.8, y = 39.5, label = "Ohio", 
           fontface = "italic", color = "black", size = 4) +
  annotate(geom = "text", x = -81, y = 38.85, label = "West Virginia", 
           fontface = "italic", color = "black", size = 4) +
  annotate(geom = "text", x = -81.95, y = 39.2, label = "Ohio River", 
           fontface = "italic", color = "navy", size = 2.5) +
  annotate(geom = "text", x = -81.5, y = 38.5, label = "Kanawha River", 
           fontface = "italic", color = "navy", size = 2.5) +
  annotate(geom = "text", x = -82, y = 39.62, label = "Muskingum River", 
           fontface = "italic", color = "navy", size = 2.5) +
  annotate(geom = "text", x = -82, y = 39.55, label = "Stockport L&D", 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.9, y = 39.5, label = "Luke Chute L&D", 
           color = "black", size = 2) +
   annotate(geom = "text", x = -81.52, y = 39.62, label = "Beverly L&D", 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.35, y = 39.55, label = "Lowell L&D", 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.65, y = 39.46, label = "Devola L&D", 
           color = "black", size = 2) +
  annotate(geom = "text", x = -84, y = 38.4, label = "Kentucky", 
           fontface = "italic", color = "black", size = 4) +
  #(geom = "text", x = -85.10, y = 39.5, label = "Indiana", 
           #fontface = "italic", color = "black", size = 4) +
  coord_sf(xlim = c(-80.8, -84.95),ylim = c(38.2, 39.9)) +
  annotation_scale(location = "bl", style = "ticks", line_col = "black", text_col = "black") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x=element_text(colour="black"),
    axis.text.y=element_text(colour="black"),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA, size=.5)
    ) # plotting the shapefiles together and adding the L&D data, labelling the L&Ds, labelling the states and rivers, plotting the average sampling locality and adding border and scalebar


River_map # Calling the map
```

\large\textbf{Figure 1. Map of the early detection and monitoring area
within the Ohio, Kanawha, and Muskingum Rivers. Black points represent Lock and Dam
facilities which create their associated pools, while red points
indicate the average of all sampling locations per pool in
`r params$YEAR`.}


\pagestyle{fancy}
\fancyhead[L,C]{}
\fancyhead[R]{\textbf{LGLFWCO: Ohio River Substation Annual Report}}
\fancyfoot[L,C]{}
\fancyfoot[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{2pt}

\newpage

```{r WI Map, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE, results='hide', out.width= '100%', fig.align="center", fig.dim=c(7,7)}
## Read in shapefiles
US_sf <- st_read("data/state.shp")
OR_sf <- st_read("data/Riverlines2.shp")

LockandDamdata <- read.csv("LockandDams.csv") # read lock and dam coordinates file

LandDdf <- data.frame(LockandDamdata) # Make csv file a df
WILandD <- setDT(LandDdf, key = 'Lock.and.Dam')[J(c("Willow Island L&D", "Hannibal L&D"))]

sf_use_s2(FALSE)
cropped <- st_crop(US_sf, xmin = -81.4, xmax = -80.77, ymin = 39.28, ymax = 39.73) # cropping the map to sampling area
#cropped_OR <- st_crop(OR_sf, xmin = -81.36, xmax = -80.8, ymin = 39.3, ymax = 39.7)

cropped_XY <- st_zm(cropped, drop = TRUE, what = "ZM") # Dropping Z coordinates
OR_sf_XY <- st_zm(OR_sf, drop = TRUE, what = "ZM") # Dropping Z coordinates

WillowIslandSites <- SamplingData %>%
  select(Site_Name, Start_Longitude, Start_Latitude, Gear_Type) %>%
  group_by(Site_Name)
WillowIslandSites <- setDT(WillowIslandSites, key = 'Site_Name')[J(c("Willow Island"))]

WillowIsland_map <- ggplot() +
  geom_sf(data = cropped_XY, size = .5, color = "grey60") +
  geom_sf(data = OR_sf_XY, size = 1.5, color = " light blue") +
  geom_point(data = WillowIslandSites, aes(x = Start_Longitude, y = Start_Latitude, color = Gear_Type), size=1.5) +
  labs(col = "Gear Type") +
  scale_color_manual(values = c("Electrofishing" = "red", "Gill Net" = "blue", "Dozer Trawl" = "magenta")) +
  geom_point(aes(x = Longitude, y = Latitude), size = 1.5, shape = 21, fill = "black", data = WILandD) +
  annotate(geom = "text", x = -80.86, y = 39.685, label = str_wrap("Hannibal L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.32, y = 39.33, label = str_wrap("Willow Island L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.3, y = 39.5, label = "Ohio", 
           fontface = "italic", color = "black", size = 4) +
  annotate(geom = "text", x = -81, y = 39.46, label = "West Virginia", 
           fontface = "italic", color = "black", size = 4) +
  annotate(geom = "text", x = -81.2, y = 39.452, label = "Ohio River", 
           fontface = "italic", color = "navy", size = 2.5) +
  #annotate(geom = "text", x = -81.5, y = 38.5, label = "Kanawha River", 
           #fontface = "italic", color = "grey60", size = 2.5) +
  coord_sf(xlim = c(-81.36, -80.8),ylim = c(39.3, 39.7)) +
  annotation_scale(location = "bl", style = "ticks", line_col = "black", text_col = "black") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x=element_text(colour="black"),
    axis.text.y=element_text(colour="black"),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA, size=.5)
    ) # plotting the shapefiles together and adding the L&D data, labelling the L&Ds, labelling the states and rivers, plotting the average sampling locality and adding border and scalebar


WillowIsland_map # Calling the map
```

\large\textbf{Figure 2. Map of the early detection and monitoring area
within Willow Island Pool. Black points represent Lock and Dam facilities
while colored points indicate each sampling location in `r params$YEAR`.
Points away from the Ohio River line indicate sampling conducted in a
tributary, backwater, or side channel.}

```{r Belleville Map, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE, results='hide', out.width= '100%', fig.align="center", fig.dim=c(7,7)}
## Read in shapefiles
US_sf <- st_read("data/state.shp")
OR_sf <- st_read("data/Riverlines2.shp")

LockandDamdata <- read.csv("LockandDams.csv") # read lock and dam coordinates file

LandDdf <- data.frame(LockandDamdata) # Make csv file a df
BellevilleLandD <- setDT(LandDdf, key = 'Lock.and.Dam')[J(c("Willow Island L&D", "Belleville L&D"))]

sf_use_s2(FALSE)
cropped <- st_crop(US_sf, xmin = -81.28, xmax = -81.785, ymin = 39.09, ymax = 39.46) # cropping the map to sampling area

cropped_XY <- st_zm(cropped, drop = TRUE, what = "ZM") # Dropping Z coordinates
OR_sf_XY <- st_zm(OR_sf, drop = TRUE, what = "ZM") # Dropping Z coordinates

BellevilleSites <- SamplingData %>%
  select(Site_Name, Start_Longitude, Start_Latitude, Gear_Type) %>%
  group_by(Site_Name) # Pulling just coords for X pool sites and gear
BellevilleSites <- setDT(BellevilleSites, key = 'Site_Name')[J(c("Belleville"))] # CHanging coords to single point


Belleville_map <- ggplot() +
  geom_sf(data = cropped_XY, size = .5, color = "grey60") +
  geom_sf(data = OR_sf_XY, size = 1.5, color = "light blue") +
  geom_point(data = BellevilleSites, aes(x = Start_Longitude, y = Start_Latitude, color = Gear_Type), size=1.5) +
  labs(col = "Gear Type") +
  scale_color_manual(values = c("Electrofishing" = "red", "Dozer Trawl" = "magenta")) +
  geom_point(aes(x = Longitude, y = Latitude), size = 1.5, shape = 21, fill = "black", data = BellevilleLandD) +
  annotate(geom = "text", x = -81.72, y = 39.13, label = str_wrap("Belleville L&D", width =3), 
           color = "black", size = 2) +
   annotate(geom = "text", x = -81.33, y = 39.33, label = str_wrap("Willow Island L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.69, y = 39.34, label = "Ohio", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -81.66, y = 39.17, label = "West Virginia", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -81.53, y = 39.30, label = "Ohio River", 
           fontface = "italic", color = "navy", size = 2.5) +
  annotate(geom = "text", x = -81.41, y = 39.43, label = "Muskingum River", 
           fontface = "italic", color = "navy", size = 2.5) +
  coord_sf(xlim = c(-81.31, -81.76),ylim = c(39.11, 39.44)) +
  annotation_scale(location = "bl", style = "ticks", line_col = "black", text_col = "black") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x=element_text(colour="black"),
    axis.text.y=element_text(colour="black"),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA, size=.5)
    ) # plotting the shapefiles together and adding the L&D data, labelling the L&Ds, labelling the states and rivers, plotting the average sampling locality and adding border and scalebar


Belleville_map # Calling the map
```

\large\textbf{Figure 3. Map of the early detection and monitoring area
within Belleville Pool. Black points represent Lock and Dam facilities
while colored points indicate each sampling location in `r params$YEAR`.
Points away from the Ohio River line indicate sampling conducted in a
tributary, backwater, or side channel.}

```{r Racine Map, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE, results='hide', out.width= '100%', fig.align="center", fig.dim=c(7,7)}
## Read in shapefiles
US_sf <- st_read("data/state.shp")
OR_sf <- st_read("data/Riverlines2.shp")

LockandDamdata <- read.csv("LockandDams.csv") # read lock and dam coordinates file

LandDdf <- data.frame(LockandDamdata) # Make csv file a df
RacineLandD <- setDT(LandDdf, key = 'Lock.and.Dam')[J(c("Racine L&D", "Belleville L&D"))]

sf_use_s2(FALSE)
cropped <- st_crop(US_sf, xmin = -81.66, xmax = -82, ymin = 38.83, ymax = 39.17) # cropping the map to sampling area

cropped_XY <- st_zm(cropped, drop = TRUE, what = "ZM") # Dropping Z coordinates
OR_sf_XY <- st_zm(OR_sf, drop = TRUE, what = "ZM") # Dropping Z coordinates

RacineSites <- SamplingData %>%
  select(Site_Name, Start_Longitude, Start_Latitude, Gear_Type) %>%
  group_by(Site_Name)
RacineSites <- setDT(RacineSites, key = 'Site_Name')[J(c("Racine"))]
#RacineSites <- st_as_sf(RacineSites, coords = c("Start_Longitude", "Start_Latitude"),
                 # crs = 4326)

Racine_map <- ggplot() +
  geom_sf(data = cropped_XY, size = .5, color = "grey60") +
  geom_sf(data = OR_sf_XY, size = 1.5, color = "light blue") +
  geom_point(data = RacineSites, aes(x = Start_Longitude, y = Start_Latitude, color = Gear_Type), size=1.5) +
  labs(col = "Gear Type") +
  scale_color_manual(values = c("Electrofishing" = "red", "Electrified Gill Net" = "green", "Gill Net" = "yellow", "Mini-Fyke Net" = "brown", "Surface Trawl" = "blue", "Dozer Trawl" = "magenta", "Hoop Net" = "orange", "Seine" = "purple")) +
  geom_point(aes(x = Longitude, y = Latitude), size = 1.5, shape = 21, fill = "black", data = RacineLandD) +
  annotate(geom = "text", x = -81.73, y = 39.135, label = str_wrap("Belleville L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.91, y = 38.93, label = str_wrap("Racine L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.84, y = 38.98, label = "Ohio", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -81.72, y = 38.97, label = "West Virginia", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -81.82, y = 39.04, label = "Ohio River", 
           fontface = "italic", color = "navy", size = 2.5) +
  annotate(geom = "text", x = -81.80, y = 38.89, label = "Mill Creek", 
           fontface = "italic", color = "grey60", size = 2.5) +
  coord_sf(xlim = c(-81.68, -81.96),ylim = c(38.85, 39.15)) +
  annotation_scale(location = "bl", style = "ticks", line_col = "black", text_col = "black") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x=element_text(colour="black"),
    axis.text.y=element_text(colour="black"),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA, size=.5)
    ) # plotting the shapefiles together and adding the L&D data, labelling the L&Ds, labelling the states and rivers, plotting the average sampling locality and adding border and scalebar


Racine_map # Calling the map
```

\large\textbf{Figure 4. Map of the early detection and monitoring area
within Racine Pool. Black points represent Lock and Dam facilities while
colored points indicate each sampling location in `r params$YEAR`. Points
away from the Ohio River line indicate sampling conducted in a
tributary, backwater, or side channel.}

```{r RC Byrd Map, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE, results='hide', out.width= '100%', fig.align="center", fig.dim=c(7,7)}
## Read in shapefiles
US_sf <- st_read("data/state.shp")
OR_sf <- st_read("data/Riverlines2.shp")

LockandDamdata <- read.csv("LockandDams.csv") # read lock and dam coordinates file

LandDdf <- data.frame(LockandDamdata) # Make csv file a df
RCByrdLandD <- setDT(LandDdf, key = 'Lock.and.Dam')[J(c("Racine L&D", "R.C. Byrd L&D"))]

sf_use_s2(FALSE)
cropped <- st_crop(US_sf, xmin = -81.86, xmax = -82.3, ymin = 38.6, ymax = 39.1) # cropping the map to sampling area

cropped_XY <- st_zm(cropped, drop = TRUE, what = "ZM") # Dropping Z coordinates
OR_sf_XY <- st_zm(OR_sf, drop = TRUE, what = "ZM") # Dropping Z coordinates

RCByrdSites <- SamplingData %>%
  select(Site_Name, Start_Longitude, Start_Latitude, Gear_Type) %>%
  group_by(Site_Name)
RCByrdSites <- setDT(RCByrdSites, key = 'Site_Name')[J(c("R.C. Byrd"))]

RCByrd_map <- ggplot() +
  geom_sf(data = cropped_XY, size = .5, color = "grey60") +
  geom_sf(data = OR_sf_XY, size = 1.5, color = "light blue") +
  geom_point(data = RCByrdSites, aes(x = Start_Longitude, y = Start_Latitude, color = Gear_Type), size=1.5) +
  labs(col = "Gear Type") +
  scale_color_manual(values = c("Electrofishing" = "red", "Electrified Gill Net" = "green", "Gill Net" = "yellow", "Mini-Fyke Net" = "brown", "Surface Trawl" = "blue", "Dozer Trawl" = "magenta", "Hoop Net" = "orange", "Seine" = "purple")) +
  geom_point(aes(x = Longitude, y = Latitude), size = 1.5, shape = 21, fill = "black", data = RCByrdLandD) +
  annotate(geom = "text", x = -82.17, y = 38.69, label = str_wrap("R.C. Byrd L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.90, y = 38.90, label = str_wrap("Racine L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -82.13, y = 39.00, label = "Ohio", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -82.03, y = 38.93, label = "West Virginia", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -82.18, y = 38.89, label = "Ohio River", 
           fontface = "italic", color = "navy", size = 2.5) +
  annotate(geom = "text", x = -82, y = 38.81, label = "Kanawha River", 
           fontface = "italic", color = "navy", size = 2.5) +
  annotate(geom = "text", x = -82.24, y = 38.71, label = "Raccoon Creek", 
           fontface = "italic", color = "grey60", size = 2.5) +
  coord_sf(xlim = c(-81.88, -82.28),ylim = c(38.66, 39.07)) +
  annotation_scale(location = "bl", style = "ticks", line_col = "black", text_col = "black") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x=element_text(colour="black"),
    axis.text.y=element_text(colour="black"),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA , size=.5)
    ) # plotting the shapefiles together and adding the L&D data, labelling the L&Ds, labelling the states and rivers, plotting the average sampling locality and adding border and scalebar


RCByrd_map # Calling the map
```

\large\textbf{Figure 5. Map of the early detection and monitoring area
within R.C. Byrd Pool. Black points represent Lock and Dam facilities
while colored points indicate each sampling location in `r params$YEAR`.
Points away from the Ohio River line indicate sampling conducted in a
tributary, backwater, or side channel.}

```{r Markland Map, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE, results='hide', out.width= '100%', fig.align="center", fig.dim=c(7,7)}
## Read in shapefiles
US_sf <- st_read("data/state.shp")
OR_sf <- st_read("data/Riverlines2.shp")

LockandDamdata <- read.csv("LockandDams.csv") # read lock and dam coordinates file

LandDdf <- data.frame(LockandDamdata) # Make csv file a df
MarklandLandD <- setDT(LandDdf, key = 'Lock.and.Dam')[J(c("Meldahl L&D", "Markland L&D"))]

sf_use_s2(FALSE)
cropped <- st_crop(US_sf, xmin = -84.1, xmax = -85.1, ymin = 38.7, ymax = 39.3) # cropping the map to sampling area

cropped_XY <- st_zm(cropped, drop = TRUE, what = "ZM") # Dropping Z coordinates
OR_sf_XY <- st_zm(OR_sf, drop = TRUE, what = "ZM") # Dropping Z coordinates

MarklandSites <- SamplingData %>%
  select(Site_Name, Start_Longitude, Start_Latitude, Gear_Type) %>%
  group_by(Site_Name)
MarklandSites <- setDT(MarklandSites, key = 'Site_Name')[J(c("Markland"))]

Markland_map <- ggplot() +
  geom_sf(data = cropped_XY, size = .5, color = "grey60") +
  geom_sf(data = OR_sf_XY, size = 1.5, color = "light blue") +
  geom_point(data = MarklandSites, aes(x = Start_Longitude, y = Start_Latitude, color = Gear_Type), size=1.5) +
  labs(col = "Gear Type") +
  scale_color_manual(values = c("Electrofishing" = "red", "Electrified Gill Net" = "green", "Surface Trawl" = "blue", "Dozer Trawl" = "magenta", "Gill Net" = "yellow", "Hoop Net" = "orange")) +
  geom_point(aes(x = Longitude, y = Latitude), size = 1.5, shape = 21, fill = "black", data = MarklandLandD) +
  annotate(geom = "text", x = -84.96, y = 38.78, label = str_wrap("Markland L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -84.171, y = 38.799, label = str_wrap("Meldahl L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -84.251, y = 39.1, label = "Ohio", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -84.613, y = 38.914, label = "Kentucky", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -84.95, y = 38.95, label = "Indiana", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -84.629, y = 39.070, label = "Ohio River", 
           fontface = "italic", color = "navy", size = 2.5) +
  annotate(geom = "text", x = -84.92, y = 38.99, label = "Laughery Creek", 
           fontface = "italic", color = "grey60", size = 2.5) +
  coord_sf(xlim = c(-84.16, -85.00),ylim = c(38.72, 39.21)) +
  annotation_scale(location = "bl", style = "ticks", line_col = "black", text_col = "black") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x=element_text(colour="black"),
    axis.text.y=element_text(colour="black"),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA , size=.5)
    ) # plotting the shapefiles together and adding the L&D data, labelling the L&Ds, labelling the states and rivers, plotting the average sampling locality and adding border and scalebar


Markland_map # Calling the map
```

\large\textbf{Figure 6. Map of the early detection and monitoring area
within Markland Pool. Black points represent Lock and Dam facilities
while colored points indicate each sampling location in `r params$YEAR`.
Sampling in this pool was in conjunction with Kentucky and Indiana state
agencies for invasive carp removal. Points away from the Ohio River line
indicate sampling conducted in a tributary, backwater, or side channel.}

```{r Open Water Map, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE, results='hide', out.width= '100%', fig.align="center", fig.dim=c(7,7)}
## Read in shapefiles
US_sf <- st_read("data/state.shp")
OR_sf <- st_read("data/Riverlines2.shp")

LockandDamdata <- read.csv("LockandDams.csv") # read lock and dam coordinates file

OpenWaterLandD <- setDT(LandDdf, key = 'Lock.and.Dam')[J(c("Winfield L&D"))]

sf_use_s2(FALSE)
cropped <- st_crop(US_sf, xmin = -81.85, xmax = -82.15, ymin = 38.5, ymax = 38.85) # cropping the map to sampling area
#cropped_OR <- st_crop(OR_sf, xmin = -81.54, xmax = -81.95, ymin = 38.2, ymax = 38.66)

cropped_XY <- st_zm(cropped, drop = TRUE, what = "ZM") # Dropping Z coordinates
OR_sf_XY <- st_zm(OR_sf, drop = TRUE, what = "ZM") # Dropping Z coordinates

OpenWaterSites <- SamplingData %>%
  select(Site_Name, Start_Longitude, Start_Latitude, Gear_Type) %>%
  group_by(Site_Name)
OpenWaterSites <- setDT(OpenWaterSites, key = 'Site_Name')[J(c("Open Water"))]

OpenWater_map <- ggplot() +
  geom_sf(data = cropped_XY, size = .5, color = "grey60") +
  geom_sf(data = OR_sf_XY, size = 1, color = "light blue") +
  geom_point(data = OpenWaterSites, aes(x = Start_Longitude, y = Start_Latitude, color = Gear_Type), size=1.5) +
  labs(col = "Gear Type") +
  scale_color_manual(values = c("Electrofishing" = "red","Electrified Gill Net" = "green", "Gill Net" = "yellow", "Surface Trawl" = "blue", "Dozer Trawl" = "magenta", "Hoop Net" = "orange")) +
  geom_point(aes(x = Longitude, y = Latitude), size = 1.5, shape = 21, fill = "black", data = OpenWaterLandD) +
  annotate(geom = "text", x = -81.90, y = 38.540, label = str_wrap("Winfield L&D", width =3), 
           color = "black", size = 2) +
  #annotate(geom = "text", x = -82.13, y = 39.00, label = "Ohio", 
           #fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -82.085, y = 38.708, label = "West Virginia", 
           fontface = "italic", color = "black", size = 3) +
  #annotate(geom = "text", x = -82.2, y = 38.89, label = "Ohio River", 
           #fontface = "italic", color = "grey60", size = 2.5) +
  annotate(geom = "text", x = -81.92, y = 38.75, label = "Kanawha River", 
           fontface = "italic", color = "navy", size = 2.5) +
  coord_sf(xlim = c(-81.87, -82.135),ylim = c(38.52, 38.83)) +
  annotation_scale(location = "bl", style = "ticks", line_col = "black", text_col = "black") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x=element_text(colour="black"),
    axis.text.y=element_text(colour="black"),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA, size=.5)
    ) # plotting the shapefiles together and adding the L&D data, labelling the L&Ds, labelling the states and rivers, plotting the average sampling locality and adding border and scalebar


OpenWater_map # Calling the map
```

\large\textbf{Figure 7. Map of the early detection and monitoring area
within Open Water Pool of the Kanawha River. Black points represent Lock
and Dam facilities while colored points indicate each sampling location
in `r params$YEAR`. Points away from the Kanawha River line indicate
sampling conducted in a tributary, backwater, or side channel.}

```{r Winfield Map, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE, results='hide', out.width= '100%', fig.align="center", fig.dim=c(7,7)}
## Read in shapefiles
US_sf <- st_read("data/state.shp")
OR_sf <- st_read("data/Riverlines2.shp")

LockandDamdata <- read.csv("LockandDams.csv") # read lock and dam coordinates file

LandDdf <- data.frame(LockandDamdata) # Make csv file a df
WinfieldLandD <- setDT(LandDdf, key = 'Lock.and.Dam')[J(c("Winfield L&D", "Marmet L&D"))]

sf_use_s2(FALSE)
cropped <- st_crop(US_sf, xmin = -81.5, xmax = -82, ymin = 38.18, ymax = 38.66) # cropping the map to sampling area
#cropped_OR <- st_crop(OR_sf, xmin = -81.54, xmax = -81.95, ymin = 38.2, ymax = 38.66)

cropped_XY <- st_zm(cropped, drop = TRUE, what = "ZM") # Dropping Z coordinates
OR_sf_XY <- st_zm(OR_sf, drop = TRUE, what = "ZM") # Dropping Z coordinates

WinfieldSites <- SamplingData %>%
  select(Site_Name, Start_Longitude, Start_Latitude, Gear_Type) %>%
  group_by(Site_Name)
WinfieldSites <- setDT(WinfieldSites, key = 'Site_Name')[J(c("Winfield"))]

Winfield_map <- ggplot() +
  geom_sf(data = cropped_XY, size = .5, color = "grey60") +
  geom_sf(data = OR_sf_XY, size = 1, color = "light blue") +
  geom_point(data = WinfieldSites, aes(x = Start_Longitude, y = Start_Latitude, color = Gear_Type), size=1.5) +
  labs(col = "Gear Type") +
  scale_color_manual(values = c("Electrofishing" = "red")) +
  geom_point(aes(x = Longitude, y = Latitude), size = 1.5, shape = 21, fill = "black", data = WinfieldLandD) +
  annotate(geom = "text", x = -81.90, y = 38.5, label = str_wrap("Winfield L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.57, y = 38.23, label = str_wrap("Marmet L&D", width =3), 
           color = "black", size = 2) +
  #annotate(geom = "text", x = -82.13, y = 39.00, label = "Ohio", 
           #fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -81.72, y = 38.4, label = "West Virginia", 
           fontface = "italic", color = "black", size = 3) +
  #annotate(geom = "text", x = -82.2, y = 38.89, label = "Ohio River", 
           #fontface = "italic", color = "grey60", size = 2.5) +
  annotate(geom = "text", x = -81.65, y = 38.30, label = "Kanawha River", 
           fontface = "italic", color = "navy", size = 2.5) +
  annotate(geom = "text", x = -81.87, y = 38.38, label = "Coal River", 
           fontface = "italic", color = "grey60", size = 2.5) +
  annotate(geom = "text", x = -81.63, y = 38.37, label = "Elk River", 
           fontface = "italic", color = "grey60", size = 2.5) +
  coord_sf(xlim = c(-81.54, -81.95),ylim = c(38.2, 38.6)) +
  annotation_scale(location = "bl", style = "ticks", line_col = "black", text_col = "black") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x=element_text(colour="black"),
    axis.text.y=element_text(colour="black"),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA, size=.5)
    ) # plotting the shapefiles together and adding the L&D data, labelling the L&Ds, labelling the states and rivers, plotting the average sampling locality and adding border and scalebar


Winfield_map # Calling the map
```

\large\textbf{Figure 8. Map of the early detection and monitoring area
within Winfield Pool of the Kanawha River. Black points represent Lock and
Dam facilities while colored points indicate each sampling location in
`r params$YEAR`. Points away from the Kanawha River line indicate
sampling conducted in a tributary, backwater, or side channel.}

```{r Lowell Map, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE, results='hide', out.width= '100%', fig.align="center", fig.dim=c(7,7)}
## Read in shapefiles
US_sf <- st_read("data/state.shp")
OR_sf <- st_read("data/Riverlines2.shp")

LockandDamdata <- read.csv("LockandDams.csv") # read lock and dam coordinates file

LandDdf <- data.frame(LockandDamdata) # Make csv file a df
LowellLandD <- setDT(LandDdf, key = 'Lock.and.Dam')[J(c("Beverly L&D", "Lowell L&D"))]

sf_use_s2(FALSE)
cropped <- st_crop(US_sf, xmin = -81.48, xmax = -81.66, ymin = 39.51, ymax = 39.57) # cropping the map to sampling area

cropped_XY <- st_zm(cropped, drop = TRUE, what = "ZM") # Dropping Z coordinates
OR_sf_XY <- st_zm(OR_sf, drop = TRUE, what = "ZM") # Dropping Z coordinates

LowellSites <- SamplingData %>%
  select(Site_Name, Start_Longitude, Start_Latitude, Gear_Type) %>%
  group_by(Site_Name) # Pulling just coords for X pool sites and gear
LowellSites <- setDT(LowellSites, key = 'Site_Name')[J(c("Lowell"))] # CHanging coords to single point

Lowell_map <- ggplot() +
  geom_sf(data = cropped_XY, size = .5, color = "grey60") +
  geom_sf(data = OR_sf_XY, size = 1.5, color = "light blue") +
  geom_point(data = LowellSites, aes(x = Start_Longitude, y = Start_Latitude, color = Gear_Type), size=1.5) +
  labs(col = "Gear Type") +
  scale_color_manual(values = c("Electrofishing" = "red", "Gill Net" = "yellow", "Hoop Net" = "orange")) +
  geom_point(aes(x = Longitude, y = Latitude), size = 1.5, shape = 21, fill = "black", data = LowellLandD) +
  annotate(geom = "text", x = -81.514, y = 39.527, label = str_wrap("Lowell L&D", width =3), 
           color = "black", size = 2) +
   annotate(geom = "text", x = -81.648, y = 39.556, label = str_wrap("Beverly L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.53, y = 39.55, label = "Ohio", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -81.61, y = 39.54, label = "Muskingum River", 
           fontface = "italic", color = "navy", size = 2.5) +
  coord_sf(xlim = c(-81.51, -81.651),ylim = c(39.515, 39.566)) +
  annotation_scale(location = "bl", style = "ticks", line_col = "black", text_col = "black") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x=element_text(colour="black"),
    axis.text.y=element_text(colour="black"),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA, size=.5)
    ) # plotting the shapefiles together and adding the L&D data, labelling the L&Ds, labelling the states and rivers, plotting the average sampling locality and adding border and scalebar


Lowell_map # Calling the map
```
\large\textbf{Figure 9. Map of the early detection and monitoring area
within Lowell Pool of the Muskingum River. Black points represent Lock and
Dam facilities while colored points indicate each sampling location in
`r params$YEAR`. Points away from the Muskingum River line indicate
sampling conducted in a tributary, backwater, or side channel.}

```{r Beverly Map, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE, results='hide', out.width= '100%', fig.align="center", fig.dim=c(7,7)}
## Read in shapefiles
US_sf <- st_read("data/state.shp")
OR_sf <- st_read("data/Riverlines2.shp")

LockandDamdata <- read.csv("LockandDams.csv") # read lock and dam coordinates file

LandDdf <- data.frame(LockandDamdata) # Make csv file a df
BeverlyLandD <- setDT(LandDdf, key = 'Lock.and.Dam')[J(c("Luke Chute L&D", "Beverly L&D"))]

sf_use_s2(FALSE)
cropped <- st_crop(US_sf, xmin = -81.63, xmax = -81.74, ymin = 39.52, ymax = 39.60) # cropping the map to sampling area

cropped_XY <- st_zm(cropped, drop = TRUE, what = "ZM") # Dropping Z coordinates
OR_sf_XY <- st_zm(OR_sf, drop = TRUE, what = "ZM") # Dropping Z coordinates

BeverlySites <- SamplingData %>%
  select(Site_Name, Start_Longitude, Start_Latitude, Gear_Type) %>%
  group_by(Site_Name) # Pulling just coords for X pool sites and gear
BeverlySites <- setDT(BeverlySites, key = 'Site_Name')[J(c("Beverly"))] # CHanging coords to single point

Beverly_map <- ggplot() +
  geom_sf(data = cropped_XY, size = .5, color = "grey60") +
  geom_sf(data = OR_sf_XY, size = 1.5, color = "light blue") +
  geom_point(data = BeverlySites, aes(x = Start_Longitude, y = Start_Latitude, color = Gear_Type), size=1.5) +
  labs(col = "Gear Type") +
  scale_color_manual(values = c("Electrofishing" = "red", "Gill Net" = "yellow", "Hoop Net" = "orange")) +
  geom_point(aes(x = Longitude, y = Latitude), size = 1.5, shape = 21, fill = "black", data = BeverlyLandD) +
  annotate(geom = "text", x = -81.721, y = 39.532, label = str_wrap("Luke Chute L&D", width =3), 
           color = "black", size = 2) +
   annotate(geom = "text", x = -81.65, y = 39.556, label = str_wrap("Beverly L&D", width =3), 
           color = "black", size = 2) +
  annotate(geom = "text", x = -81.68, y = 39.55, label = "Ohio", 
           fontface = "italic", color = "black", size = 3) +
  annotate(geom = "text", x = -81.697, y = 39.58, label = "Muskingum River", 
           fontface = "italic", color = "navy", size = 2.5) +
  coord_sf(xlim = c(-81.64, -81.73),ylim = c(39.525, 39.594)) +
  annotation_scale(location = "bl", style = "ticks", line_col = "black", text_col = "black") +
  theme(
    panel.background = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    axis.text.x=element_text(colour="black"),
    axis.text.y=element_text(colour="black"),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.line = element_line(colour = "black"),
    panel.border = element_rect(colour = "black", fill=NA, size=.5)
    ) # plotting the shapefiles together and adding the L&D data, labelling the L&Ds, labelling the states and rivers, plotting the average sampling locality and adding border and scalebar


Beverly_map # Calling the map
```

\large\textbf{Figure 10. Map of the early detection and monitoring area
within Beverly Pool of the Muskingum River. Black points represent Lock and
Dam facilities while colored points indicate each sampling location in
`r params$YEAR`. Points away from the Muskingum River line indicate
sampling conducted in a tributary, backwater, or side channel.}

\newpage

\selectfont\large\textbf{Methods and Results} \vspace{.5cm}

\selectfont\large This substation implements a multi-gear sampling
effort to maximize the detection and capture of invasive carp in the Ohio River where little-to-no densities occur. We applied a random survey design for main and side channel sites and a fixed survey design for tributary and backwater sites (Table 1). Environmental and biological data are collected at each sampling site and consist of surface temperature (°C), dissolved oxygen (mg/L), conductivity ($\mu$S/cm), dominant substrate type, species identification to common name, and length (mm). All invasive carp encountered had additional biological data of weight (g) and sex collected.

In `r params$YEAR`, a total of `r Site_Data %>% group_by(Gear) %>% summarise() %>% nrow() %>% words()` unique gear types, `r GearData %>% group_by(Gear_Type) %>% summarise() %>% pluck('Gear_Type')`, were utilized across `r Site_Info %>% nrow()` sampling sites (Table 2). The type of gear deployed was determined by suitable habitat and gear type restrictions per site. Electrofishing efforts ranged from `r min(EFData$EF_ShockTime_seconds, na.rm=TRUE)` seconds (`r round(min(EFData$EF_ShockTime_seconds, na.rm=TRUE)/60)` minutes) to `r max(EFData$EF_ShockTime_seconds, na.rm=TRUE)` seconds (`r round(max(EFData$EF_ShockTime_seconds, na.rm=TRUE)/60)` minutes) with an average shock time of `r round(mean(EFData$EF_ShockTime_seconds, na.rm=TRUE))` seconds
(`r round(mean(EFData$EF_ShockTime_seconds, na.rm=TRUE)/60)` minutes). Deployed Gill Nets were approximately 300 or 150 feet in total length and varied in mesh size (4, 5 or 6 inch) and depth (6, 10 or 24 feet). Gill Nets are typically deployed for a minimum of 2 hours. Electrified Gill Net is a method that uses electricity to guide fish into a deployed Gill Net. This method is best used to directly target a group of fish, i.e., a school of invasive carp, with time and distance of sampling varying upon the site location.

**There were a total of
`r sum(Count_Data[which(Count_Data$Count_Common_Name == 'Bighead Carp' | Count_Data$Count_Common_Name =='Silver Carp' | Count_Data$Count_Common_Name =='Grass Carp'), 4])` invasive carp captured in `r params$YEAR` with
`r Joint_Data %>% group_by(Site_Name) %>% filter( Site_Name %in% c("Winfield", "Racine", "Belleville", "Willow Island")) %>% filter(Count_Common_Name %in% c("Bighead Carp", "Silver Carp", "Grass Carp")) %>% nrow()`
caught above R.C. Byrd Pool.** Total catch summaries for each of pool can be found in Appendix 1.

\vspace{.5cm}

\large\textbf{Table 1. Number of surveys conducted per pool by habitat
type in `r params$YEAR`.} \vspace{.5cm}

```{r habitat table, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE}
Site_Info$Count <- 1

Site_Table <-
  aggregate(Count ~ Strata + Site_Name, data = Site_Info, FUN = sum) %>% # aggregate data by species and pool
  as.data.frame() %>% # Neccessary? Makes it a dataframe
  spread(, key = Strata, value = Count, fill = NA, drop = TRUE) %>% # Spreads the pool name out to columns instead of rows
  adorn_totals(where = c("row", "col")) %>%
  rename("Pool Name" = "Site_Name")
  
Site_Table[is.na(Site_Table)] <- "" # change NA values to blank space
Site_Table

kbl(Site_Table, booktabs = T,align = "lccccc", valign = "middle",linesep = "", centering = T) %>%
  add_header_above(c(" ", "Habitat Type" = 5)) %>%
kable_styling(font_size = 12, latex_options = c("striped", "hold_position"), stripe_color = "#d9d9d9") %>% 
row_spec(0, italic = T, bold=T) # creates table
```

```{=tex}
\vspace{.5cm}
\newpage
```
\large\textbf{Table 2. Number of surveys conducted per pool by gear
type in `r params$YEAR`.} \vspace{.5cm}

```{r gear table, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE}
GearData$Count <- 1

Gear_Table <-
  aggregate(Count ~ Gear_Type + Site_Name, data = GearData, FUN = sum) %>% # aggregate data by gear and pool
  as.data.frame() %>% # Neccessary? Makes it a dataframe
  spread(, key = Gear_Type, value = Count, fill = NA, drop = TRUE) %>%# Spreads the pool name out to columns instead of rows
  adorn_totals(where = c("row", "col")) %>%
  rename("Pool Name" = "Site_Name")

Gear_Table[is.na(Gear_Table)] <- "" # change NA values to blank space
Gear_Table

kbl(Gear_Table, booktabs = T,align = "lcccccc", valign = "middle",linesep = "", centering = T) %>%
  add_header_above(c(" ", "Gear Type" = 9)) %>%
kable_styling(font_size = 12, latex_options = c("striped", "hold_position", "scale_down"), stripe_color = "#d9d9d9") %>% 
row_spec(0, italic = T, bold=T) # creates table
```

\vspace{.5cm}

\large\textbf{Table 3. Surveys with successful invasive carp captures `r params$YEAR`. }
\vspace{.5cm}

```{r Carp table, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE}
Joint_Data$Number <- as.numeric(Joint_Data$Number)
Carp_Data <- Joint_Data %>%
  #select(Count_Common_Name, Number, Gear, Stream_Name, Site_Name) %>%
  filter(Count_Common_Name %in% c("Bighead Carp", "Silver Carp", "Grass Carp")) %>%
  rename("Species" = "Count_Common_Name") %>%
  rename("Total Caught" = "Number") %>%
  rename("Gear Type" = "Gear") %>%
  rename("Tributary Name" = "Stream_Name") %>%
  rename("Pool Name" = "Site_Name")

Carp_Data <- Carp_Data[,-c(2,3,4,5,6)]
Carp_Data <- Carp_Data[, c(1,2,3,4,5,6)]

kbl(Carp_Data, booktabs = T,align = "lcccc", valign = "middle",linesep = "") %>%
kable_styling(font_size = 12, latex_options = c("striped", "hold_position", "scale_down"), stripe_color = "#d9d9d9") %>% 
row_spec(0, italic = T, bold=T) # creates table
```

```{=tex}
\vspace{.5cm}
\newpage
```
\selectfont\large\textbf{Partnership Support}

Our office provides sampling assistance to state, federal, and Universities as part of a collaborative effort with local partners. Support was provided for both invasive carp specific projects and other various projects including native species. We plan on continuing to aide our partners in a wide range of projects as we grow staff and contacts in the area. \textbf{The following was additional sampling assistance provided in `r params$YEAR`:} \vspace{.5cm}

\textbf {Agency- U.S. Fish and Wildlife Service:}

-   Worked with LGLFWCO staff to conduct eDNA sampling within Ohio River
    tributaries in West Virginia and Pennsylvania waters
    -   300 samples collected across Tombleson Run, Little MIll Creek, Mill Creek and Sandy
        Creek of Racine pool
          - Total of four positive hits: two Bighead Carp (*Hypophthalmichthys nobilis*) detections in Mill Creek, one Bighead Carp and one invasive carp detection in Tombleson Run
    -   100 samples collected in both Raccoon Creek and Beaver River in
        Montgomery pool with zero positive detections
    -   100 samples collected in Little Beaver Creek in New Cumberland
        pool with zero positive detections
    -   100 samples collected within Winfield pool in Armor Lake, Coal River and
        the Pocatalico River with zero positive detections
-   Assisted Carterville FWCO with tagging invasive carp in the Cannelton pool of the Ohio
    River
    -   200 invasive carp tagged in Markland Pool (200 Silver Carp, *Hypophthalmichthys molitrix*)
-   Assisted Ohio River Islands National Wildlife Refuge with their
    annual mussel surveys
    -   Staff spent multiple days operating as boat captain and dive
        tender
    -   Assisted on tender boat for a multi-agency mussel survey
-   Staff from Maryland FWCO assisted with our community surveys
-   Assisted Green Bay FWCO with Ruffe (*Gymnocephalus cernua*) surveys in Little bay de Noc

\textbf{Northeast Fishery Center:}

-   Collecting fin clips of fish for validation of DNA markers for metabarcoding

\textbf{Agency- West Virginia Department of Natural Resources:}

-   Completed a joint effort in Raccoon Creek and the old lock chambers
    within R.C. Byrd pool to tag invasive carp
    -   Utilized overnight gill net sets in old lock chambers and gill net sets in Raccoon Creek to
        capture and tag invasive carp
    -   Three Silver Carp caught in WVDNR nets
    -   One Bighead Carp caught in USFWS nets
-   Conducted surveys for presence absence of invasive carp
-   Assisted with Paddlefish (*Polyodon spathula*) egg mats in Middle Island Creek
-   Assisted with Catfish surveys in Winfield pool
-   Assisted with community surveys in R.C. Byrd pool
-   Assisted with surface trawl surveys for young-of-year presence/absence of invasive carp

\textbf{Agency- West Virginia University:}

-   Conducted surveys in Willow Island pool for community size spectra
    analysis
-   Deployed gill nets to target American Paddlefish with Dr. Welsh in Raccoon Creek of R.C. Byrd pool
    -   One Bighead Carp and two Silver Carp were caught and tagged by Dr. Welsh

\textbf{Agency- Kentucky Department of Fish and Wildlife:}

-   Conducted an invasive carp removal event through electrofishing and
    gill netting for otolith removal
    -   1 Bighead Carp and 55 Silver Carp were removed and otoliths
        were collected

\textbf{Agency- Pennsylvannia Fish and Boat Commission:}

-   Assisted with identifying and counting species caught from surveys from 2023


\newpage
\KOMAoptions{paper=landscape, DIV=25}
\fancypagestyle{plain}{}
\pagestyle{empty}

\large\textbf{Appendix 1. Number of fish caught per pool in
`r params$YEAR`.} \vspace{.5cm}

```{r fish table, message=FALSE, error=FALSE, warning=FALSE, echo= FALSE}
Joint_Data$Number <- as.numeric(Joint_Data$Number)
Fish_Table <- 
  aggregate(Number ~ Count_Common_Name + Site_Name, data = Joint_Data, FUN = sum) %>% # aggregate data by species and pool
  as.data.frame() %>% # Neccessary? Makes it a dataframe
  spread(, key = Site_Name, value = Number, fill = NA, drop = TRUE) %>% # Spreads the pool name out to columns instead of rows
  rename("Species" = "Count_Common_Name") #rename column name

Fish_Table <- Fish_Table[, c(1,3,5,6,2,7,4,8,9,10)]
Fish_Table <- Fish_Table %>%
  mutate_at(c(2:6), as.numeric) %>%
  adorn_totals(where = c("row", "col"), na.rm = TRUE) # totals up fish by pool
Fish_Table[is.na(Fish_Table)] <- "" # change NA values to blank space
Fish_Table

kbl(Fish_Table, booktabs = T,align = "lccccc", valign = "middle",linesep = "", longtable = TRUE) %>%
kable_styling(font_size = 12, latex_options = c("striped", "repeat_header"), fixed_thead = TRUE, stripe_color = "#d9d9d9") %>% 
  footnote(general = "Centrarchid, Clupeid, Cyprinid and Moxostoma spp. are individuals that species could not be confirmed due to specimen being larval or to small", alphabet =("Bold rows are invasive species"), threeparttable = TRUE) %>%
row_spec(0, italic = T, bold=T) %>% # creates table
  row_spec(3, bold =T) %>%
  #row_spec(33, bold =T) %>%
  row_spec(57, bold =T)
#number=("Unknowns are individuals waiting on species confirmation by WVU."),
```
\thispagestyle{empty}